Model Finding for (Co)recursive Functions in SMT\thanks{ This research is partially supported by the Inria technological development action ``Contre-exemples Utilisables par Isabelle et Coq'' (CUIC). }

### 2015-05-05 tex/main.tex
more

\newcommand{\vthinspace}{\kern+0.083333em}
\newcommand{\typ}[1]{^{\vthinspace #1}}

@@

The procedure $\conv$ in Figure~\ref{fig:encoding} translates the $\Sigma$-formula
$\varphi$ into an $\extendsig{\Sigma}$-formula.
This calls the subprocedure $\conv_0$, which takes two arguments:\ the term $t$
to translate and a \emph{polarity} $p$ (either $\ptrue$, $\pfalse$, or
$\pnone$). It returns a pair $( r,\, D )$, where $r$ is a term of
type $\tau$ and $D$ is a set of formulas.
\jb{Explain r and D here briefly.}
%The role of $D$ is to ensure that
%the (restricted) function definition for $\con{f}$ includes certain tuples in
%its domain, which we explain more in the following.

The translation modifies $\varphi$ in two main ways. First, it restricts the
quantification on function definitions for $\con{f}$ to the corresponding
uninterpreted type $\fargsort{\con{f}}$ and inserts appropriate . Second, it augments $\varphi$ with
additional constraints of the form $\exists z\typ{\fargsort{\con{f}}}. (
\vecfarg{\con{f}}( z ) \teq \vec t )$ which ensure that this restriction for
the defintion $\con{f}$ covers all relevant tuples of terms, namely the ones
for which an $\con{f}$-application exists and is relevant to the satisfiability
of the current branch of $\varphi$.

>>>>

\newcommand{\negvthinspace}{\kern-0.083333em}
\newcommand{\vthinspace}{\kern+0.083333em}
\newcommand{\typ}[1]{^{\vthinspace #1}}

@@

The procedure $\conv$ in Figure~\ref{fig:encoding} translates the $\Sigma$-formula
$\varphi$ into an $\extendsig{\Sigma}$-formula.
This calls the subprocedure $\conv_0$, which takes two arguments:\ the term $t$
to translate and a \emph{polarity} $p$ (either $\ptrue$, $\pfalse$, or
$\pnone$). It returns a pair $( t'\negvthinspace,\, D )$, where $t'$ is a term of
type $\tau$ and $D$ is a set of formulas encoding additional constraints.
%The role of $D$ is to ensure that
%the (restricted) function definition for $\con{f}$ includes certain tuples in
%its domain, which we explain more in the following.

The translation modifies $\varphi$ in two main ways. First, it restricts the
quantification on function definitions for $\con{f}$ to the corresponding
uninterpreted type $\fargsort{\con{f}}$ and inserts appropriate coercions
$\fargx{\con{f}}{i}$. Second, it augments $\varphi$ with additional constraints
$\exists z : \fargsort{\con{f}}.\;\, \vecfarg{\con{f}}( z ) \teq \vec t$; these
ensure that the restricted definition for $\con{f}$ covers all relevant tuples
of terms, namely the ones for which an $\con{f}$ application exists and is
relevant to the satisfiability of the current branch of $\varphi$.
\jb{what does ``current branch of'' mean? can we drop it / rephrase it / vague
it up?}
